---
title: "Assignment 1"
author: "SUMIT DUTT MISHRA"
date: "11/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message =  FALSE)
```
## Importing Packages
```{r}
library(ISLR)
library(dplyr)
library(ggplot2)
```

Only three variables are loaded into the Carseats dataset.
Filtering the data into two categories based on where it's kept on the shelf (GOOD or BAD).

```{r}
SafeBabies <- Carseats %>% select("Sales", "Price", "ShelveLoc")
Good_shevles <- filter(SafeBabies, ShelveLoc == "Good")
Bad_shevles <- filter(SafeBabies, ShelveLoc == "Bad")
```

###Building a Linear Regression model to forecast car seat sales for both good and bad shelve locations separately.

```{r}
#Linear Model for GOOD Shelve location
Lm_Good <- lm(Sales ~ Price, data = Good_shevles)
summary(Lm_Good)
```

```{r}
#Linear Model for BAD Shelve location
lm_Bad <-lm(Sales ~ Price, data = Bad_shevles)
summary(lm_Bad)
```

###Equation:
Total Profit = Sales * (selling price  - Production Cost)

We generated the following formula as a result of the equation's further implications:

Best selling price  = Predicted Sales based on Production Cost / (2 * Estimated Price Coefficient)

Assuming a CarSeat's production cost is $55.0, the CarSeat's best selling price  is as follows.

## Best cost for shelve location Good ##
```{r}
Productioncost<-55
paste("The best price for a good shelf location", ((-Lm_Good$coefficients[[2]] *Productioncost) + (Lm_Good$coefficients[[1]]))/(-2 * Lm_Good$coefficients[[2]]))
```
## Best cost for shelve location bad ##
```{r}
paste("The best price for a bad shelf position", ((-lm_Bad$coefficients[[2]] *Productioncost) + (lm_Bad$coefficients[[1]]))/(-2 * lm_Bad$coefficients[[2]]))
```
Note: The negative mark is inserted into the denominator to eliminate the resistance, as the LM symbol indicates a negative correlation between Price and Breakdown (Sales).

Here the variation in Production Cost from $40 to $85 and the selling price  also varies as below.

```{r}
Good_Optimal_price_Range <- (predict(Lm_Good, data.frame(Price = c(40:85)))) / (-2*Lm_Good$coefficients[2])
Bad_Optimal_Price_Range <- (predict(lm_Bad, data.frame(Price = c(40:85)))) / (-2*lm_Bad$coefficients[2])
```

selling price  for Good and Bad Shelve Locations over Production Costs of $40-$85

```{r}
Price_Range<- cbind.data.frame(Production_Cost = c(40:85), Selling_Price_Good = Good_Optimal_price_Range, Selling_Price_Bad = Bad_Optimal_Price_Range)
Price_Range
```

Price differences in both good and bad shelf areas are shown in the graph below.

```{r}
ggplot(Price_Range, aes(Production_Cost, Price_Range)) + geom_line(aes(y = Good_Optimal_price_Range, col = "Good Shelve")) + geom_line(aes(y = Bad_Optimal_Price_Range, col = "Bad Shelve"))
```


